Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-11-18 version3/version3.tex
added classical literature

		To build the mathematical model, we followed the standard strategy developed in the literature concerning SIR models.
		We assume that individuals in $S$ can be infected by both members of $A$ and $I$.
		We suppose that the individuals in the $A$ and $I$ compartments may have different contact rates $\beta_A$ and $\beta_I$, and different recovery rates $\gamma_A$ and $\gamma_I$.
		Furthermore, we consider a rate $\delta$ at which individuals in $A$ may develop symptoms or are otherwise detected and so will move to the $I$ compartment.
		Lastly, we assume that only members of $S$ and $A$ are mobile.

@@

	\textbf{Acknowledgments:} \\
	\textbf{Funding:}
	This research was funded by the Socially Responsible Modeling, Computation, and Design (SoReMo) Initiative, through the Illinois Institute of Technology. \\
	\textbf{Conflicts of Interest:}
	Author states no conflict of interest. \\

>>>>

		To build the mathematical model, we followed the standard strategy developed in the literature concerning SIR models \cite{bio-models}.
		We assume that individuals in $S$ can be infected by both members of $A$ and $I$.
		We suppose that the individuals in the $A$ and $I$ compartments may have different contact rates $\beta_A$ and $\beta_I$, and different recovery rates $\gamma_A$ and $\gamma_I$.
		Furthermore, we consider a rate $\delta$ at which individuals in $A$ may develop symptoms or are otherwise detected and so will move to the $I$ compartment.
		Lastly, we assume that only members of $S$ and $A$ are mobile.

@@

	\textbf{Acknowledgments:} \\
	\textbf{Funding:}
	This research was funded by the Socially Responsible Modeling, Computation, and Design (SoReMo) Initiative, at the Illinois Institute of Technology. \\
	\textbf{Conflicts of Interest:}
	Author states no conflict of interest. \\
